%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Quantum Mob} % Organization
    {Toronto, ON} % Location
    {August 2019 - Novemeber 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized the latest React, Redux and server side rendering best practices to help build a large scale closed-source component library for LoyaltyOne Canada.}
        \item {Built pixel-perfect components from Zeplin wireframe specs and performed unit tests with Jest, React Testing Library, and Storybook.}
        \item {Contributed to web-based internal Quantum Mob tooling (e.g. a large automated drip campaign email service) using Typescript, TypeORM, Redux, and NextJS.}
         \item {Helped build a complex Chrome extension for pixel tracking Gmail email reads, replies, and message content. Integrated this service with the aforementioned drip campaign's back end.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Clausehound} % Organization
    {Toronto, ON} % Location
    { August 2018 - August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built scalable, reusable, and highly interactive functional React components that derived their state from a complex RxJS pipeline (flux architecture) and interfaced with a PHP7 backend via GraphQL.}
        \item {Consistently delivered large features, taking ownership through every step of the process. Implemented a real-time legal contract search, a major update that turned static legal contracts into dynamically editable legal documents, and e-signature integration from scratch.}
        \item {Dev ops responsibilities included setting up and maintaining up Bitbucket pipelines for continuous integration with Docker containers and push-to-deploy (staging and production).}
         \item {Built a Google Sheets extension with a polished (Material) UI that integrated with the Clausehound contract API for the purpose of streamlining how users edit and share filled legal documents at scale.}
         \item {Worked closely with back end engineers and CTO on higher level problems within the application, e.g. type architecture and GraphQL schemas.}
         \item {Received invaluable mentorship in functional programming, composability, clean code, and design patterns (Joshua Koudys, CTO).}
      \end{cvitems}
    }
%
\end{cventries}
