%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Personal Side Project} % Role
    {myriad ({\tiny https://github.com/jonathandannel/myriad)})} % Event
    {} % Location
    {December 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A single page React app running on a Node (Express) backend that aims to use ML and computer vision (with the tensorflow.js wrapper and face-api.js) to make homemade passport and visa photos a breeze.}
        \item{Project built from scratch, utilizing architectural best practices picked up from a combination of work experience and self-driven research/experimentation.}
        \item{Tools used include Webpack, Babel, Sequelize, JSON Web Tokens, Material UI, Redux, React Router (for hash routing - API and client exist on the same server), webcam streaming, and more. Currently a work in progress.}
      \end{cvitems}
    }

\cventry
    {Lighthouse Labs Demo Day}
    {Sketched Out ({\tiny https://github.com/jonathandannel/sketched-out})}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
        \item {A real-time browser drawing game that combines creativity, competition, and social interactivity to make for a fun and addicting experience. Built with Node and React, this app makes heavy use of websockets and the HTML 5 Canvas API.}
        \item {Contributed mostly to canvas drawing functionality and message passing over websockets.}
        \item{Project took first place at Demo Day, where it received a surprising amount of interest from guests. }
        \item{Other open-source side projects available on https://github.com/jonathandannel}
      \end{cvitems}
    }
    
\end{cventries}


